---
output: html_document
---

```{r setup-command, include=FALSE, warning=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
```

## Git Commands 


* Generally you will be working on the `main` or `master` branch
* `<file>` must include file name and the extension (i.e. 'test.sas' or 'test.R' not just 'test')

```{r}
tribble(
          ~command, ~description
    , "`git status`"               , "see which files have been changed/added/deleted on working branch"
    , "`git add --all`"            , "stage ALL files that have been changed/added/deleted"
    , "`git log -<numb>`"          , "View a list of the most recent `<numb>` commits; e.g. `git log -2` will show 2 commits"
    , "`git add <file>`"           , "Stage a specific `<file>`"
    , "`git commit -m '<message>'`", "Commit changes with short `<message>`"
    , "`git push origin <branch>`" , "Push to specific `<branch>`; will generally be `main` or `master`"
    , "`git pull origin <branch>`" , "Pull from specific `<branch>`; will generally be `main` or `master`"
    , "`git fetch origin <branch>`", "See if there are any changes/updates from a specific `<branch>`; could do this prior to `git pull`"
    , "`git diff <file>`"          , "View changes for a specific `<file>`; if you just use `git diff` all changes for all files will be shown. If you have a lot of changes it will end with an `(END)` on the screen, to quit this screen press the `Q` key"
    , "`git diff --stat --cached origin/<branch>`", "List of files that have been commited (list of files that will be included in next `git push`)"
    , "`git reset`"                , "Undo `git add`; will un-stage all files; can also use `git reset <file>` to unstage specific file"
  ) %>%
  #put in alphabetical order 
  arrange(command) %>% 
  #escape = F --> allows conversion of html code
  #ex make cell grey
  #         escape = F --> NA     (in grey font)
  #         escape = T --> <span style=" color: grey !important;" >NA</span>
  kable(escape = F, label = "Git Commands") %>%
  kable_styling(
     bootstrap_options = c(
         "hover" #highlight row when hover over it 
        , full_width = FALSE #doesn't have to be full width 
      )
  )
```

**What if I want to ignore any differences on my clone and 'reset' to the version on GitHub?** 

1. `git fetch origin`  
This will get the most recent versions from GitHub  
1. `git reset --hard origin/<branch>`  
This will change all files in your clone repository to match the most up-to-date version from GitHub  

This should be done rarely because any changes you have worked on will not be saved.  


## UNIX Commands  

In addition to git command, you can use UNIX commands in the bash window.  

```{r}
tribble(
          ~command, ~description
    , "`ls -l`"   , "View files in current folder and their recent mondification"
    , "`cd <folder>`", "Move down into a specific folder; e.g. go from `C:/Documents` to `C:/Documents/<folder>`" 
    , "`cd ..`", "Move up one folder; e.g. go from `C:/Documents/<folder>` to `C:/Documents`"
  ) %>%
  #put in alphabetical order 
  arrange(command) %>%
  #escape = F --> allows conversion of html code
  #ex make cell grey
  #         escape = F --> NA     (in grey font)
  #         escape = T --> <span style=" color: grey !important;" >NA</span>
  kable(escape = F) %>%
  kable_styling(
     bootstrap_options = c(
         "hover" #highlight row when hover over it 
        , full_width = FALSE #doesn't have to be full width 
      )
  )
```



